---
title: "HW1_EX2"
author: "Mara"
date: "3/8/2023"
output: html_document
---

## EXERCISE 2 - FINANCIAL ANALYSIS

__Questions 1 and 2__ 
```{r,echo=FALSE, message=FALSE, warning=FALSE}
library(quantmod)
```


```{r}
mydates <- c("01/01/2022","01/01/2023")

mydates2 <- as.Date(mydates, format = "%m/%d/%Y")
mydates2

getSymbols("AAPL", from = min(mydates2), to = max(mydates2))
getSymbols("CSCO", from = min(mydates2), to = max(mydates2))
getSymbols("INTC", from = min(mydates2), to = max(mydates2))
getSymbols("HD", from = min(mydates2), to = max(mydates2))
getSymbols("GOOG", from = min(mydates2), to = max(mydates2))
getSymbols("JPM", from = min(mydates2), to = max(mydates2))
```

__Question3:__
```{r}
plot(AAPL$AAPL.Close)
plot(CSCO$CSCO.Close)
```


__Question 4__
```{r}
mydatesnew <- c("10/01/2022","01/01/2023")
mydates3 <- as.Date(mydatesnew, format = "%m/%d/%Y")
mydates3

getSymbols("GOOG", from = min(mydates3), to = max(mydates3))
getSymbols("JPM", from = min(mydates3), to = max(mydates3))

candleChart(GOOG, theme = 'white', type = 'candles')
candleChart(JPM, theme = 'white', type = 'candles')
```

__Question 5__
```{r}
mean(AAPL$AAPL.Close)
mean(GOOG$GOOG.Close)
mean(JPM$JPM.Close)
mean(CSCO$CSCO.Close)
mean(INTC$INTC.Close)
mean(HD$HD.Close)

var(AAPL$AAPL.Close)
var(GOOG$GOOG.Close)
var(JPM$JPM.Close)
var(CSCO$CSCO.Close)
var(INTC$INTC.Close)
var(HD$HD.Close)
```

__Question 6__
```{r}
mean(AAPL$AAPL.Close)
mean(GOOG$GOOG.Close)
mean(JPM$JPM.Close)
mean(CSCO$CSCO.Close)
mean(INTC$INTC.Close)
mean(HD$HD.Close)

sd(AAPL$AAPL.Close)
sd(AAPL$AAPL.Close)
sd(GOOG$GOOG.Close)
sd(JPM$JPM.Close)
sd(CSCO$CSCO.Close)
sd(INTC$INTC.Close)
sd(HD$HD.Close)
```

__Question 7__
```{r,echo=FALSE,message=FALSE,warning=FALSE}
library(PerformanceAnalytics)
```

```{r,echo=FALSE}
mydates = c("01/01/13", "01/01/23")
mydates2013 <- as.Date(mydates, format = "%m/%d/%y")
library(quantmod)
library(PerformanceAnalytics)
```

```{r}
getSymbols("AAPL", from = min(mydates2013), to = max(mydates2013))
getSymbols("CSCO", from = min(mydates2013), to = max(mydates2013))
getSymbols("INTC", from = min(mydates2013), to = max(mydates2013))
getSymbols("HD", from = min(mydates2013), to = max(mydates2013))
getSymbols("GOOG", from = min(mydates2013), to = max(mydates2013))
getSymbols("JPM", from = min(mydates2013), to = max(mydates2013))

AAPL_returns <- na.omit(ClCl(AAPL))
GOOG_returns <- na.omit(ClCl(GOOG))
CSCO_returns <- na.omit(ClCl(CSCO))
INTC_returns <- na.omit(ClCl(INTC))
HD_returns <- na.omit(ClCl(HD))
JPM_returns <- na.omit(ClCl(JPM))
Rf <- 0.03/(252)
```

```{r}
mean(AAPL_returns) 
mean(GOOG_returns)
mean(CSCO_returns)
mean(INTC_returns)
mean(HD_returns)
mean(JPM_returns)


sd(AAPL_returns) 
sd(GOOG_returns)
sd(CSCO_returns)
sd(INTC_returns)
sd(HD_returns)
sd(JPM_returns)
```

```{r}
sharpe_ratioAAPL <- (mean(AAPL_returns) - Rf) / sd(AAPL_returns) * sqrt(252)
sharpe_ratioGOOG <- (mean(GOOG_returns) - Rf) / sd(GOOG_returns) * sqrt(252)
sharpe_ratioCSCO <- (mean(CSCO_returns) - Rf)/sd(CSCO_returns) * sqrt(252)
sharpe_ratioINTC <- (mean(INTC_returns) - Rf )/ sd(INTC_returns) * sqrt(252)
sharpe_ratioHD <- (mean(HD_returns)- Rf) / sd(HD_returns) * sqrt(252)
sharpe_ratioJPM <- (mean(JPM_returns)- Rf) / sd(JPM_returns) * sqrt(252)
```

```{r}
cat("Sharpe Ratios for each stock:")
print(sharpe_ratioAAPL)
print(sharpe_ratioGOOG) 
print(sharpe_ratioCSCO) 
print(sharpe_ratioINTC)
print(sharpe_ratioHD)
print(sharpe_ratioJPM)
```

```{r}
AAPL_return = quantmod::dailyReturn(AAPL)
CSCO_return = quantmod::dailyReturn(CSCO)
INTC_return = quantmod::dailyReturn(INTC)
HD_return = quantmod::dailyReturn(HD)
GOOG_return = quantmod::dailyReturn(GOOG)
JPM_return = quantmod::dailyReturn(JPM)
```

```{r}
#excess return
AAPL_excess = AAPL_return - 0.03/252
CSCO_excess = CSCO_return - 0.03/252
INTC_excess = INTC_return - 0.03/252
GOOG_excess = GOOG_return - 0.03/252
JPM_excess = JPM_return - 0.03/252
HD_excess = HD_return - 0.03/252
```

```{r}
#yearly sharpe ratio
AAPL_sharpe_yearly = mean(AAPL_excess) / sd(AAPL_excess) * sqrt(252)
CSCO_sharpe_yearly = mean(CSCO_excess) / sd(CSCO_excess) * sqrt(252)
INTC_sharpe_yearly = mean(INTC_excess) / sd(INTC_excess) * sqrt(252)
HD_sharpe_yearly = mean(HD_excess) / sd(HD_excess) * sqrt(252)
GOOG_sharpe_yearly = mean(GOOG_excess) / sd(GOOG_excess) * sqrt(252)
JPM_sharpe_yearly = mean(JPM_excess) / sd(JPM_excess) * sqrt(252)

yearly_shape = cbind(AAPL_sharpe_yearly, CSCO_sharpe_yearly, INTC_sharpe_yearly, HD_sharpe_yearly, GOOG_sharpe_yearly, JPM_sharpe_yearly)

colnames(yearly_shape) = c("AAPL", "CSCO", "INTC", "HD", "GOOG", "JPM")
yearly_shape
``` 

```{r}
#estimation of mean (mu) and variance (Sigma)
mat_return = cbind(AAPL_return, CSCO_return, INTC_return, HD_return, GOOG_return, JPM_return)
colnames (mat_return) = c("AAPL", "CSCO", "INTC", "HD", "GOOG", "JPM")

mu = apply(mat_return, 2, mean)
Sigma = var(mat_return)


# equally weighted portfolio
equal_return = (AAPL_return + CSCO_return + INTC_return + HD_return + GOOG_return + JPM_return)/6

muequal = mean(equal_return)
varequal = var(equal_return)

#The individual variance of these 6 stocks are:
diag(Sigma)
```


__Question 8__

```{r}
# find optimal weights
one = rep(1,6)
inv_Sigma = solve(Sigma)
W = as.numeric(inv_Sigma %*% one / as.numeric(t(one) %*% inv_Sigma %*% one))
names(W) = c("AAPL", "CSCO", "INTC", "HD", "GOOG", "JPM")
```

```{r}
# optimal portfolio
optim_return = AAPL_return*W[1] + CSCO_return*W[2] + INTC_return*W[3] + HD_return*W[4] + GOOG_return*W[5] + JPM_return*W[6]
mu_optim = mean(optim_return)
var_optim = var(optim_return)
```

So the optimal weights for each individual stocks are:

```{r}
W
```

Moreover, the variance of this optimally weighted portfolio is r round(var_optim,6), which is even smaller than the varaince of the equally weighted portfolio (r round(var_equal,6)). 

```{r}
investment_summary = matrix(NA, 2, 8)
dimnames(investment_summary)[[1]] = c("Expected value", "Variance")
dimnames(investment_summary)[[2]] = c("AAPL", "CSCO", "INTC", "HD", "GOOG", "JPM", "Equal", "Min var")
investment_summary[1, ] = c(mu, mu_equal, mu_optim)
investment_summary[2, ] = c(diag(Sigma), var_equal, var_optim)
investment_summary
```

```{r}
plot(sqrt(investment_summary[2, ]), investment_summary[1, ], 
     ylab = "Daily Expected Value of Investment", 
     xlab = "Daily Investment Standard Deviation", 
     pch = 19, cex = 1, lty = "solid", lwd = 2, 
     xlim = c(min(sqrt(investment_summary[2, ])), max(sqrt(investment_summary[2, ])+3e-03)), 
     col = 1:8)
grid()
text(sqrt(investment_summary[2, ]), investment_summary[1, ], 
     labels = names(investment_summary[1, ]), cex= 0.7, pos = 4)
```

As we can see from the graph, the equally weighted portfolio performs well in general in the sense that it has relatively high investment output and low investment risk. But the portfolio which minimizes the investment risk can do even better with higher investment output.
